%\documentclass[dvipdfm,final]{pittetd}%   If you want to use dvipdfm. The file is to be normally processed (LaTeX), and 
%                                   then the program dvipdfm applied to it. This will create the PDF file with bookmarks
%                                   and links. It will also try to convert any PS graphics included.
\documentclass[pdftex,final]{pittetd}   % If you want to use PDFLaTeX instead. This will create the PDF file directly.
%                                   Processing time can be longer. No PS graphics conversion will take place 
%                                   automatically.
%
%Other options: ma, ms, for Master's. 
%11pt, 10pt, font size (12pt is default). 
%final, makes pittetd's warnings (about things that might go against the Format Guidelines) 
%into error messages. 
%Option 'sectionletters' numbers the chapters with Roman numerals (I, II, etc.), sections with 
%letters (A, B), subsections with numbers (1, 2), and subsubsections with lowercase letters (a, b). 
%The four levels of the enumerate environment receive the same treatment. Within the
%text, however, cross references (\ref} produce `the whole thing,' something like I.A.1 
%instead of only 1.
%
\usewithpatch{graphicx}%            Better \usewithpatch than \usepackage because it makes pittetd look for any 
%                                   available patch for the package. 
\usepackage{afterpage}
\usepackage{listings}
\usepackage[linesnumbered]{algorithm2e}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath,amsthm}%        But you can't use \usewithpatch for several packages as in this line. The search for
%                                   patches has to be then forced through:
\patch{amsmatch}
\patch{amsthm}
%
%\patch{pittdiss}                   If you started writing your thesis with the pittdiss class, this patch makes 
%                                   pittetd interpret pittdiss commands.
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\renewcommand\thesubfigure{(\alph{subfigure})}
%\patch{pitthesis}                  Analogous for the pitthesis class.
\title[Adaptive and Power-aware Fault Tolerance for Future Extreme-scale Computing]{Adaptive and Power-aware Fault Tolerance for Future Extreme-scale Computing}% The optional argument is the %                                   version of the title that will appear in Acrobat Reader's Document Info dialog box.
\author{Xiaolong Cui}
\degree{B.E. in Computer Science, Xi'an Jiaotong University, 2012 \\ M.S. in Computer Science, University of Pittsburgh, 2017}
%\date{July 20th 1967}%             This date is the date of the thesis defense. Default is \today
\year{2017}                        %pittetd will use the current year unless otherwise indicated. So this command is not
%                                   necessary.
\keywords{Extreme-scale computing, Forward recovery, Reliability, Fault tolerance, Shadow Replication, Leaping}% This list appears in the field 'Keywords' of Acrobat Reader's Document Info
%                                   dialog box, and also, optionally, after the abstract.
\subject{Adaptive and Power-aware Fault Tolerance for Future Extreme-scale Computing}%              This fills in the 'Subject' field in Acrobat Reader's Document Info dialog box.
\school{School of Computing and Information}%    The name of the school will be preceeded by 'the' unless otherwise specified, as in:
%\school[certain]{Department of Computer Science}
%
%\chapterfloats%                    Un-comment this to get figures and tables numbered within chapters.
\begin{document}
\maketitle
%
% For the committee membership page, you have to provide the names and affiliations of the members. The first one will 
% be treated by pittetd as the committee chair (thesis/dissertation advisor).
\committeemember{Dr. Taieb Znati, Departmental of Computer Science, University of Pittsburgh}
\coadvisor{Co-advisor: Dr. Rami Melhem, Department of Computer Science, University of Pittsburgh}%         This is used if there are two advisors.
\committeemember{Dr. Rami Melhem, Department of Computer Science, University of Pittsburgh}%         This is used if there are two advisors.
\committeemember{Dr. John Lange, Department of Computer Science, University of Pittsburgh}
\committeemember{Dr. Esteban Meneses, School of Computing, Costa Rica Institute of Technology} 
% etc., as many as needed. For master's theses, the committee may be omitted, naming only the advisor.
\
% etc., as many as needed. For master's theses, the committee may be omitted, naming only the advisor.
%\school{Department of Computer Science}
\makecommittee
\copyrightpage        %             Uncomment this to get a copyright page.
\begin{abstract}
Two major trends in large-scale computing are the rapid growth in HPC with in particular an international exascale initiative, and the dramatic expansion of Cloud infrastructures accompanied by the Big Data passion. To satisfy the continuous demands for increasing computing capacity, future extreme-scale systems will embrace a multi-fold increase in the number of computing, storage, and communication components, in order to support an unprecedented level of parallelism. Despite the capacity and economies benefits, making the upward transformation to extreme-scale poses numerous scientific and technological challenges, two of which are the power consumption and fault tolerance. With the increase in system scale, failure would become a norm rather than an exception, driving the system to significantly lower efficiency with unforeseen power consumption.

This thesis aims at simultaneously addressing the above two challenges by introducing a novel fault-tolerant computational model, referred to as \textit{Leaping Shadows}. Based on Shadow Replication, Leaping Shadows associates with each main process a suite of coordinated shadow processes, which execute in parallel but at differential rates, to deal with failures and meet the QoS requirements of the underlying application under strict power/energy constraints. In failure-prone extreme-scale computing environments, this new model addresses the limitations of the basic Shadow Replication model, and achieves adaptive and power-aware fault tolerance that is more time and energy efficient than existing techniques. 

In this thesis, we first present an analytical model based optimization framework that demonstrates Shadow Replication's adaptivity and flexibility in achieving multi-dimensional QoS requirements. Then, we introduce Leaping Shadows as a novel power-aware fault tolerance model, which tolerates multiple types of failures, guarantees forward progress, and maintains consistent level of resilience. Lastly, the details of a Leaping Shadows implementation in MPI is discussed, along with extensive performance evaluation that includes comparison to checkpoint/restart. Collectively, these efforts advocate an adaptive and power-aware fault tolerance alternative for future extreme-scale computing.


\end{abstract}
% If you say \begin{abstract}[Keywords:] instead of the simple \begin{abstract}, a list of the keywords is appended.
% The list comes from the \keywords command above.
% The starred version \begin{abstract*} typesets the word `ABSTRACT' on the top of the page
\tableofcontents
\listoftables                     % Pittetd will complain if you tell it to create a list of tables when there are no
%                                   tables (as in this sample file). Uncomment this command if you have tables.
\listoffigures                    % Obvious analogous for figures.
\preface
\vfill
\begin{center}
\textit{For my beloved families.} 
\end{center}
\vfill
% This is the text of the preface, with acknowledgments, dedication, etc. It is optional, and you create, as shown, by 
% just saying \preface and starting the preface's actual text. Note that 'foreword' is no longer acceptable as title
% for this preliminary.
%
%Conventions, such as notation (nomenclature) and abbreviations, don't receive their own preliminary page. They can be included as an appendix, or as part of the introduction.
\chapter{INTRODUCTION}
\label{chapter:intro}
\input{Chapters/intro}

\chapter{BACKGROUND}
\label{chapter:background}
\input{Chapters/background}

\chapter{Shadow Replication}
\label{chapter:shadowing}
\input{Chapters/shadowing}

\chapter{Reward-based optimal Shadow Replication}
\label{chapter:reward}
\input{Chapters/reward}

\chapter{Leaping Shadows}
\label{chapter:scale}
\input{Chapters/scale}

\chapter{Tolerance of Silent data corruption}
\label{chapter:sdc}
\input{Chapters/sdc}

\chapter{\texorpdfstring{\MakeLowercase{rs}MPI}{rsMPI}: an implementation in MPI}
\label{chapter:implementation}
\input{Chapters/implementation}

\chapter{Conclusion}
\label{chapter:summary}
\input{Chapters/summary}



%%
%\chapter{Introduction}%             And when you type '\chapter', pittetd understands that this is the body of the 
%%                                   document. 
%We begin by saying that we do not really have much to say, but for the sake of clarity we divide our topic in chapters.
%
%\chapter{Second chapter}
%The topics treated in this chapter can be somewhat obscure. For humanitarian considerations, the chapter will be subdivided.
%\section{FIRST SECTION}%            Remember to capitalize the sections (otherwise, the bookmark will be lowercase)
%The topic treated here, given its complexity, merits an additional subdivision.
%\subsection{First subsection of the section}
%This is well-known topic, and we shall discuss it no more.
%\subsection{Second subsection of the section}
%This is a very complicated topic and we shall discuss it in our next paper.
%\chapter{Conclusions}
%This is the second chapter of the present dissertation. It is more interesting than the first one, for it is the last one.
%
%\appendix                          After this command, chapters will be formatted as appendices. For example:
%\chapter{Raw data}
%
\bibliographystyle{abbrv}
\safebibliography{main}       %   \safebibliography is used the same way as \bibliography, but gives pittetd
%                                   a greater chance to succeed in formatting the bibliography when non-standard
%                                   BibTeX styles are used.
%\begin{singlespace}
%\bibliographystyle{plainnat}
%{
%\footnotesize
%\bibliography{main}
%}
%\end{singlespace}
\end{document}
